On Secure Delegation of SampBQP with a Classical Client

### 2020-02-29 bqp.tex
Fix grammar

Next, we make the verifier completely classical by compiling $\Piblind$ using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
It was originally used to compile $\PiMF$ into $\PiMFZ$ to allow a purely classical client,
but it can be applied to other $\QPIP_1$ protocols such as our $\Piblind$.
We give a high-level overview of our compiliation results.

>>>>

Next, we make the verifier completely classical by compiling $\Piblind$ using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
It was originally used to compile $\PiMF$ into $\PiMFZ$ to allow a purely classical client,
but in fact can be applied to other $\QPIP_1$ protocols such as our $\Piblind$.
We give a high-level overview of our compiliation results.
